%!TEX root = ../cv_teacher.tex

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{RESEARCH EXPERIENCE}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Graduate Researcher} % Job title
    {NUIST} % Organization
    {2017 - present} % Date(s)
    {}%{Advisor: Yan Yin} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {PI of the Postgraduate Research \& Practice Innovation Program of Jiangsu Province "Estimation of Lightning Nitrogen Oxides" (grant no. KYCX20\_0922).}
        \item {Participant of the National Natural Science Foundation of China (Major Program) "The Impacts and Mechanisms of Convective Transportation and Lightning on Vertical Distribution of Atmospheric Components" (grant no. 91644224).}
        \item {Participant of the National Natural Science Foundation of China (Major Program) "Observation and Parameterization of Atmospheric Ice Nucleating Particles over the Northern China Plain and Their Effects on Cloud and Precipitation" (grant no. 41590873).}
        \item {Participant of the National Natural Science Foundation of China (General Program) "Influence of Inland Vessel Emissions on Air Pollution" (grant no. 41590873).}
        \item {Developing the lightning nitrogen oxides retrieval algorithm based on a high‑resolution chemical model (WRF‑Chem).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {KNMI} % Organization
    {2021 - 2022} % Date(s)
    {}%{Advisor: Ronald van der A} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Estimating the lifetime and emissions of lightning nitrogen oxides using satellite observations (OMI, TROPOMI).}
        % \item {Identification of lightning NO$_2$ using satellite observations (TROPOMI, VIIRS) and ground lightning datasets.}
        % \item {Estimating the lightning NO$_2$ lifetime and production efficiency in the Arctic.}
        % \item {Evaluating NO$_x$ emissions from different sectors in the Arctic.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {NUIST} % Organization
    {2016 - 2017} % Date(s)
    {}%{Advisors: Yan Yin} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluating the effects of deep convection on ozone profiles using satellite observations.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Undergraduate Researcher} % Job title
%     {NUIST} % Organization
%     {2013 - 2016} % Date(s)
%     {Advisors: Zhuang Wang} % Advisor
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Investigating the ecotoxicological effects of nano-titanium nitride with dissolved organic matter.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}
