%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{RESEARCH EXPERIENCE}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {KNMI} % Organization
    {2021 - 2022} % Date(s)
    {Advisor: Ronald van der A} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Identification of lightning NO$_2$ using satellite observations (TROPOMI, VIIRS) and ground lightning datasets.}
        \item {Estimating the lightning NO$_2$ lifetime and production efficiency in the Arctic.}
        \item {Evaluating NO$_x$ emissions from different sectors in the Arctic.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Researcher} % Job title
    {NUIST} % Organization
    {2017 - present} % Date(s)
    {Advisor: Yan Yin} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing the OMI lightning NO$_x$ retrieval algorithm based on a high-resolution chemical model (WRF-Chem).}
        \item {Diagnosing the upper-tropospheric O$_3$ and NO$_x$ budget affected by convection in southeastern China
        through the combination of a field campaign (ground-based radar, lightning networks, and ozonesondes), satellite data, and models.}
        \item {Analyzing the relationship among lightning activity, cloud top height, and vertical velocity using geostationary satellite observations (GOES-16 ABI \& GLM).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {NUIST} % Organization
    {2016 - 2017} % Date(s)
    {Advisors: Yan Yin} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluating the effects of deep convection on O$_3$ profiles using satellite observations (MLS, FY-2) and reanalysis data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {NUIST} % Organization
    {2013 - 2016} % Date(s)
    {Advisors: Zhuang Wang} % Advisor
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigating the ecotoxicological effects of nano-titanium nitride (TiN) with dissolved organic matter.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
