%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\clearpage
\cvsection{PRESENTATIONS}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpublications}

%---------------------------------------------------------
\publication
{(poster) Lightning NO$_2$ in the Arctic,
\emph{2022 Dragon 5 Mid-term Results Symposium},
online, October 2022.} % Title
{2022} % Date(s)

%---------------------------------------------------------
\publication
{(invited oral) Processing EO satellite data with Pytroll,
\emph{Lunch Talk},
KNMI, De Bilt, the Netherlands, July 2022.} % Title
{2022} % Date(s)

%---------------------------------------------------------
\publication
{(oral) Arctic lightning and anthropogenic NO$_x$ emissions estimated from TROPOMI observations,
\emph{EGU General Assembly 2022},
Vienna, Austria, May 2022.} % Title
{2022} % Date(s)

%---------------------------------------------------------
\publication
{(invited oral) Python for meteorology,
\emph{Atmospheric Physics \& Environment Workshop},
NUIST, Nanjing, China, October 2022.} % Title
{2022} % Date(s)

%---------------------------------------------------------
\publication
{(oral) Influence of convection on the upper-tropospheric O$_3$ and NO$_x$ budget in southeastern China,
\emph{Aerosols, Clouds, Precipitation and Climate (ACPC) Workshop},
online, May 2022.} % Title
{2022} % Date(s)

%---------------------------------------------------------
\publication
{(invited oral) Git tutorial,
\emph{Atmospheric Physics \& Environment Workshop},
NUIST, Nanjing, China, May 2022.} % Title
{2022} % Date(s)

%---------------------------------------------------------
\publication
{(oral) Estimates of lightning NO$_x$ production based on high-resolution OMI NO$_2$ retrievals over the continental United States,
\emph{100th American Meteorological Society Annual Meeting},
Boston, MA., USA, January 2020.} % Title
{2020} % Date(s)

% %---------------------------------------------------------
% \publication
% {Estimates of lightning NO$_x$ production based on high-resolution OMI NO$_2$ retrievals over the continental United States (poster),
% \emph{8th COAA International Conference on Atmosphere, Ocean, and Climate Change (ICAOCC)},
% Nanjing, Jiangsu, China, July 2019.} % Title
% {2019} % Date(s)

%---------------------------------------------------------
\publication
{(poster) Estimates of lightning NO$_x$ production based on high-resolution OMI NO$_2$ retrievals over the continental United States,
\emph{EGU General Assembly 2019},
Vienna, Austria, April 2019.} % Title
{2019} % Date(s)

%---------------------------------------------------------
\end{cvpublications}
